Title?

### 2016-11-08 draft.tex
Trivial change to title.
I'm an idiot

>>>>

This calculation was done in Ref.~\cite{Dent:2012mx} Using the one-pion exchange model of nucleon-nucleon interactions\footnote{There is also some question as to the applicability of this approach in this regime. Pionless effective field theory techniques developed for low-energy nucleons might provide a more accurate answer; this may be considered in a later paper} they largely followed the form of the calculation of the axionic bremsstrahlung rate [brinkmann/turner/iwamoto], in which the axion is taken to be massless. Considering the energy scales in the problem, this is clearly a reasonable approximation when dealing with axion masses on the order of $ 10^-3 $ eV; it is less clear that it is still appropriate when dealing with dark photon masses on the order of 10-100 MeV. We therefore reproduce the calculation without making that simplifying assumption, and see if it has an effect on the result. We find that it does indeed quite dramatically change the excluded region in $ \eps-m_A $ space, increasing the lower bound by some two orders of magnitude and opening up a considerable portion of the parameter space.
